A Comparison of Graph Processing Systems

### 2020-09-15 documentation/paper/sections/preliminiaries.tex
weitere kleine Änderungen

\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{pull style} there is only one write and many read operations. Thus locks can be avoided. So \emph{push-style} operators are more efficient, if there are only a few \emph{active} vertices or edges at the same time, or the \emph{neighborhoods} do not overlap, which can not be avoided in general. On the other hand \emph{pull-style} operators are more efficient, if there are many \emph{active} vertices or edges at the same time.

>>>>

\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{push style} there is only one write and many read operations. Thus locks can be avoided. So \emph{push-style} operators are more efficient, if there are only a few \emph{active} vertices or edges at the same time, or the \emph{neighborhoods} do not overlap, which can not be avoided in general. On the other hand \emph{pull-style} operators are more efficient, if there are many \emph{active} vertices or edges at the same time.
